%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Authors: Jonas Nygaard Eriksen
% Encoding: UTF8
% LaTeX File for CV
% Last modified: January 5, 2015
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Setting up the document class
\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%\usepackage{cmbright}

% Setting up document geometry
\usepackage[left=2cm,right=2cm,top=3cm,bottom=3cm]{geometry}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.1}
\usepackage{microtype}

% Setting up page numbering
\usepackage{lastpage}
\cfoot{\addressfont\itshape\textcolor{gray}{Page \thepage\ of \pageref{LastPage}}}

% Allowing for multicolumn section
\usepackage{multicol}

% Declaring new commands
\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
\DeclareRobustCommand*\mit{\@fontswitch\relax\mathnormal}

% Setting up the CV style and color
\moderncvstyle{banking}
\moderncvcolor{black}

% Setting up title and contact information
\name{Jonas}{Nygaard Eriksen}
\title{CV}
\address{Fuglesangs Allé 4, DK-8210 Aarhus V}{Building 2622, Office 213}
\phone{+4587166024}
\email{jeriksen@econ.au.dk}
\homepage{au.dk/en/jeriksen@econ.au.dk}
\social[linkedin]{jonasnygaarderiksen}
%\social[twitter]{JonasNygaard}
\social[github]{JonasNygaard}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
%\quote{Some quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN MATTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makecvtitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PERSONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal information}
\cventry{}{January 21, 1988}{Date of birth}{}{}{}
\cventry{}{Danish}{Nationality}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\cventry{September 2012-present}
        {Department of Economics and Business, Aarhus University and CREATES}
        {Ph.D. in Economics and Business}
        {Aarhus, Denmark} 
        {}
        {Advisors: Stig Vinther Møller and Charlotte Christiansen}

\cventry{September 2014-December 2014}
        {Cass Business School, City University London}
        {Visiting Graduate Student}
        {London, England}
        {}
        {Host: Reader in Finance Maik Schmeling}

\cventry{September 2010-August 2012}
        {School of Business and Social Sciences, Aarhus University}
        {MSc. in Finance}
        {Aarhus, Denmark}
        {GPA: 11.5}
        {Thesis: The output gap, consumption-based asset pricing, and the cross-sectional risk premia on stocks and bonds.}

\cventry{Juli 2009-December 2009}
        {Instituto Tecnol{\'o}gico de Estudios Superiores de Monterrey (ITESM)}
        {Exchange student}
        {Monterrey, Mexico}
        {}
        {}

\cventry{September 2007-July 2010}
        {School of Business and Social Sciences, Aarhus University}
        {BSc. in Business Administration}
        {Aarhus, Denmark}
        {GPA: 10.1}
        {Thesis: Forudsigelse af aktiemarkedet: En in-sample og out-of-sample undersøgelse af det aggregerede danske aktiemarked.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACADEMIC EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Experience}

\cventry{Fall 2014}
        {Applied Econometric Methods I and II}
        {Guest lecturing}
        {Aarhus University}
        {Master's course}
        {Responsible for two complete lectures with one being based on my own research.}

\cventry{Spring 2013,2014,2015}
        {HA and eocon programs}
        {Supervision of Bachelor Theses}
        {Aarhus University}
        {}
        {Supervision of bachelor theses in the field of financial economics and asset pricing.}

\cventry{Fall 2010-present}
        {Responsible for exercise sessions and assignments in the following courses:}
        {Teaching Assistant}
        {Aarhus University}
        {}
        {\begin{itemize}
        \item Applied Econometric Methods I and II (Fall 2011,2012,2013)
        \item Operations and Supply Chain Management (Spring 2011)
        \item Costing Theory and Capital Budgeting (Fall 2010)
        \end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESEARCH PAPERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Research Papers}

\cventry{2014}
        {Peer review. Published in \textit{Journal of Banking and Finance}, Vol. 49, pp. 459–468}
        {Forecasting US Recessions: The Role of Sentiment}
        {Aarhus University}
        {}
        {Joint work with Charlotte Christiansen and Stig Vinther Møller.}

\cventry{2014}
        {Working paper}
        {Expected Business Conditions and Bond Risk Premia}
        {Aarhus University}
        {}
        {Single authored.}

\cventry{2014}
        {Working paper}
        {Global Economic Activity and Expected Returns}
        {Aarhus University}
        {}
        {Joint work with Maik Schmeling and Christian Wagner.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% RESEARCH INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Interest}

\begin{multicols}{2}
    \begin{itemize}
        \item Financial Economics
        \item Time Series Econometrics
        \item Empirical Finance
        \item Asset Pricing
        \item Asset Return Predictability
        \item Forecasting
    \end{itemize}
\end{multicols}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% OTHER ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Other Activities}

\cventry{2013}
        {AUPA}
        {Vice-President of Aarhus University's Ph.D. Association}
        {Aarhus University}
        {}
        {}

\cventry{2013-present}
        {PHABUSS}
        {President Ph.D. Association at School of Business and Social Sciences}
        {Aarhus University}
        {}
        {}

\cventry{2013-present}
        {}
        {Member of the Finance Research Group}
        {Aarhus University}
        {}
        {}




\end{document}